---
title: " 10 R Code Challenges for Beginners "
output: 
  html_document: 
    number_sections: yes
---

# Create an array of matrixes

In R, a matrix is a collection of elements of the same data type arranged in a fixed number of rows and columns. A vector is the simplest type of data collection, which consists of a collection of things.

For this challenge, you need to write code in R that'll create an array of two 3x3 matrixes from two given numeric vectors of different lengths. Each matrix will have 3 rows and 3 columns.

```{r create an array of matrixes}

```


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
