---
title: " 10 R Code Challenges for Beginners "
output: 
  html_document: 
    number_sections: yes
---

# Create an array of matrixes

In R, a matrix is a collection of elements of the same data type arranged in a fixed number of rows and columns. A vector is the simplest type of data collection, which consists of a collection of things.

For this challenge, you need to write code in R that'll create an array of two 3x3 matrixes from two given numeric vectors of different lengths. Each matrix will have 3 rows and 3 columns.

```{r create an array of matrixes}
# these are two numeric vectors of different lengths
vec_a <- c(4, 3, 1, 9, 6, 3, 2, 9, 10)
vec_b <- c(129, 131, 443, 123)

# creating 3x3 matrixes from those numeric vectors
mat_a <- matrix(vec_a, nrow = 3, ncol = 3)
mat_b <- matrix(vec_b, nrow = 3, ncol = 3)

# viewing the matrixes
mat_a
mat_b

# creating an array of those matrixes
array <- matrix(c(mat_a, mat_b), ncol = 3, nrow = 6)
array
```


# Create a list with different types

A list in R is an object with heterogeneous elements. A list can consist of many kinds of objects, including matrixes, functions, or even data frames.

For this challenge, create a list with R containing two vectors, one simply x and the other of 100 random integers, and print the results.

```{r create a list with different types}
a_list <- list("x", sample(c(21:35), size = 100, replace = TRUE))
a_list
```


tes 

tes lagi
